ongo data cleaning

### 2023-03-25 data-cleanning/data_cleaning_ongo.Rmd
Update data_cleaning_ongo.Rmd

@@

For the `still_active` variable, the values are manually input for the blank lines. After checking against the offical website, `FALSE` for those have indeed de-register and `TRUE` for those that turned out to be parsing errors. The rest NAs will be recoded to `TRUE` in data cleaning.

@@

Dummy variable indicating whether the official sponsoring unit (for registration and annual audit) is at the national or local level. 
It is clearly correlated with `geo_scope_num`, but should be a mediating factor for the relationship we are examine.

@@

A related `multiple_index` is a index number created to identify siblings, in the form of 100-1, 100-2...(starting from 100 to ensure all have three digits) `NA` for ONGOs only having one RO. Note there can be cases where one of the siblings has been de-registered, but only several.

`work_field_code1` is the main work field code
`work_field_code2` is an alternative code for the work field if the ONGO's works touch on overlapping fields

The field categories are (planed to be) decided based on Article 3 of the law.

**to be discussed**
Some confusing one - plan to mark -> google translate -> discuss/decide together

@@

@@

**Decided by how the work fields of registered NGOs cluster**

@@

(Chinese background) (ONGOs set up by Chinese communities abroad or by Chinese entities in foreign jurisdictions). Such ONGOs tend to have strong local connection with its origins. Not sure yet if should be kept as a separate variable. Now coded only in work_field_code2. 
(equality)
Only in `work_field_code2`, aim to right-based Charity and humanitarian and non-right-based Charity and humanitarian orgs

>>>>

Kept the above chunks here, expecting there might be changes in the manual coding csv file, especially for the "need check" area coding

@@

For the `still_active` variable, the values are manually input for the blank lines. After checking against the official website, `FALSE` for those have indeed de-register and `TRUE` for those that turned out to be parsing errors. The rest NAs will be recoded to `TRUE` in data cleaning.

@@

Dummy variable indicating whether the official sponsoring unit (for registration and annual audit) is at the national or local level. 
It is clearly correlated with `geo_scope_num`, but should be a mediating factor for the relationship we are examining.

@@

A related `multiple_index` is an index number created to identify siblings, in the form of 100-1, 100-2...(starting from 100 to ensure all have three digits) `NA` for ONGOs only having one RO. Note there can be cases where one of the siblings has been de-registered, but only several.

@@

`work_field_code1` is the main work field code
`work_field_code2` is an alternative code for the work field if the ONGO's work touches on overlapping fields

The field categories listed on Article 3 of the law.

**Cross checking of ONGO work field coding**
Google translation of the work field statements (disclosed in Chinese) are included. Researcher 1 is the main coder of the work field. When there is some ambiguity of the coding, Researcher 1 marks "TRUE" in the `coding_need_check` document and Researcher 2 cross check the coding of the work field.

@@

**Decided by how the work fields of registered NGO ROs cluster**

@@

(Chinese background) (ONGOs set up by Chinese communities abroad or by Chinese entities in foreign jurisdictions). Such ONGOs tend to have strong local connection with its origins. Not sure yet if should be kept as a separate variable. Now coded only in work_field_code2. 
(equality)

Only in `work_field_code2`, aim to right-based Charity and humanitarian and non-right-based Charity and humanitarian orgs
